Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-01-20 ms.tex
deleted the now duplicated dispersion offset figure and moved that caption info to the other figures

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{tser_LWSW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
\caption{Time series of the simultaneous SW/LW Time Series Stability test
}\label{fig:otisLWSWtser}
\end{figure*}

The locations of the subarrays have ROWCORNER=431.
This means there are not top or bottom reference pixels.
If we use a horizontally-displaced background region, the pre-amp offsets will not be properly subtracted.
We therefore subtract the median from each column and then each row (not including the grism aperture).
We subtract the median of each column first to remove the amplifier offsets and then the median of each row second to reduce the 1/f noise.
Figure \ref{fig:otisLWSWtserShift} shows the dramatic effect of subtracting the columns and rows from each aperture.

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{raw_tser_LWgrisMPPVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Slope Images}
\fig{raw_tser_LWgrisMMMRowColSubVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Column-by-column and row-by-row subtraction}}
\caption{The grism time series contains correlated read noise due to pre-amplifier offsets over each amplifier and 1/f noise in the horizontal (fast read) direction.
Row-by-row-subtraction dramatically decreases the noise due to 1/f noise while column-by-column subtraction dramatically decreases the pre-amplifier offset noise.
}\label{fig:otisLWSWtserShift}
\end{figure*}

@@

\begin{figure*}
\gridline{\fig{spec_offsets_o9LEDwf322w2Flat_NRCN83-256-O9LW.pdf}{0.49\textwidth}{}}
\caption{The position variations along the dispersion direction for this time series test are two orders of magnitude larger than expectation for flight.
}\label{fig:otisWavebinTSeries}
\end{figure*}

>>>>

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{tser_LWSW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
\caption{Time series of the simultaneous SW/LW Time Series Stability test.
The image motion in this test due to vibrations and oscillations is two orders of magnitude larger than expeced in flight.
The complicated PSF and low signal on the short wavelength channel compromise its sensitivity whereas the long wavelength broadband flux is dominated by lamp instability.
}\label{fig:otisLWSWtser}
\end{figure*}

The locations of the subarrays have ROWCORNER=431.
This means there are not top or bottom reference pixels.
If we use a horizontally-displaced background region, the pre-amp offsets will not be properly subtracted.
We therefore subtract the median from each column and then each row (not including the grism aperture).
We subtract the median of each column first to remove the amplifier offsets and then the median of each row second to reduce the 1/f noise.
Figure \ref{fig:otisLWcolrowSub} shows the dramatic effect of subtracting the columns and rows from each aperture.

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{raw_tser_LWgrisMPPVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Slope Images}
\fig{raw_tser_LWgrisMMMRowColSubVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Column-by-column and row-by-row subtraction}}
\caption{The grism time series contains correlated read noise due to pre-amplifier offsets over each amplifier and 1/f noise in the horizontal (fast read) direction.
Row-by-row-subtraction dramatically decreases the noise due to 1/f noise while column-by-column subtraction dramatically decreases the pre-amplifier offset noise.
}\label{fig:otisLWcolrowSub}
\end{figure*}

@@
